\section*{General Introduction}
\addcontentsline{toc}{section}{General Introduction}

Modern organizations face the challenge of managing diverse business processes that are often fragmented across different tools and departments.  
An \textbf{Enterprise Resource Planning (ERP)} system addresses this issue by providing a unified platform to streamline operations such as human resources, sales (POS), finance, and inventory management.  

This project focuses on the development of a customized ERP solution for \textbf{Anter's Lab}.  
My role in this project was as the \textbf{backend developer}, in charge of designing and implementing the complete server-side logic.  
The backend was structured as a collection of \textbf{RESTful APIs} developed using the \textbf{Laravel framework}, secured with \textbf{JWT authentication}, and supported by a \textbf{MySQL database}.  
For testing and validation, \textbf{Postman} was extensively used to ensure robust and reliable endpoints.  
The development environment was based on \textbf{Visual Studio Code}, with \textbf{GitLab} used for version control and collaborative management.  

The project was conducted using the \textbf{Agile methodology}, following the \textbf{Scrum framework}. The work was divided into iterative \textbf{sprints}, with regular reviews and adaptations.  
\textbf{ClickUp} was employed as the project management tool to organize tasks, assign responsibilities, and monitor sprint progress.  

The remainder of this report is structured as follows:
\begin{itemize}
    \item Chapter 1 presents Anter's Lab and the context of the project.
    \item Chapter 2 details the requirements analysis and functional specifications.
    \item Chapter 3 describes the system design and architectural choices.
    \item Chapter 4 explains the backend implementation, technologies used, and development sprints.
    \item The conclusion summarizes the contributions and suggests perspectives for future improvements.
\end{itemize}
